My title

### 2022-01-28 outputs/paper/paper.Rmd
test2

@@

For the purpose of the paper, the analysis will focus on the fire incidents occurred in cooking areas or kitchens. Moreover, the author is interested in exploring the relationship between the estimated dollar loss and the fire alarm system operation among the selected kitchen fire incidents. To do so, the author uses Tidyverse [@citetidyverse] to select the variables of "Area of Origin", "Fire Alarm System Operation", "Latitude", "Longitude", and "Estimated Dollar Loss". The author also removes all entrants with missing values for any of the variables. The following shows an extract of the cleaned dataset (Table \@ref(tab:dataextract))

@@

```{r dataextract}
fire_incidents <-
  read.csv(file = "inputs/data/fire_incidents.csv")

>>>>

install.packages("ggmap")
install.packages("mapproj")

@@

For the purpose of the paper, the analysis will focus on the fire incidents occurred in cooking areas or kitchens. Moreover, the author is interested in exploring the relationship between the estimated dollar loss and the fire alarm system operation among the selected kitchen fire incidents. To do so, the author uses Tidyverse [@citetidyverse] to select the variables of "Area of Origin", "Fire Alarm System Operation", "Latitude", "Longitude", and "Estimated Dollar Loss". The author also removes all entrants with missing values for any of the variables. The following shows an extract of the cleaned dataset (Table \@ref(tab:dataextract)).

@@

```{r dataextract}
fire_incidents <-
  read_csv("~/Session1/STA304_Paper_1/inputs/data/fire_incidents.csv")
